---
title: "Data Science - Week 6"
author: "Fay Bennett"
date: "04/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```

```{r packages}
library(tidyverse)
```

# Introduction:
We decided to analyze if there is a difference between chaffinch sex and mass.

# Methods:
We compared the difference between chaffinch sex and mass using RStudio and RMarkdown.

# Results:

# Discussion:



<!-- # Importing the dataset: -->
chaff <- read.table("chaff.txt", header = TRUE)

<!-- tidying the data -->
chaff<- chaff%>% 
  pivot_longer(names_to = "sex", 
               values_to = "mass",
               cols = everything())

file <-  "chaff.txt"
write.table(chaff, 
            file, 
            quote = FALSE,
            row.names = FALSE)

<!-- calculating the SS(x) of all the mass values: -->
sum_sq <- function(df, measure, group) {
  df %>% group_by({{ group }}) %>% 
    summarise(ss = sum(({{measure}} - mean({{measure}}))^2))
}

sum_sq(chaff, mass, sex)
<!-- sex        ss -->
  <!-- <fct>   <dbl> -->
<!-- 1 females  86.8 -->
<!-- 2 males    87.9 -->

<!-- Summarising the data: -->
chaff_summary <- chaff %>% 
  group_by(sex) %>% 
  summarise(mean_index = mean(mass),
            n = length(mass),
            sd = sd(mass),
            se = sd/sqrt(n))

<!-- Creating a summary function: -->
chaffsummaryfunc <- function(ds, measure, group) {
  chaff %>% group_by(sex) %>% 
  summarise(mean_mass = mean(mass),
            n = length(mass),
            sd = sd(mass),
            se = sd/sqrt(n))
}
chaffsummaryfunc(chaff, mass, sex)
 <!-- sex     mean_mass     n    sd    se -->
  <!-- <fct>       <dbl> <int> <dbl> <dbl> -->
<!-- 1 females      20.5    20  2.14 0.478 -->
<!-- 2 males        22.3    20  2.15 0.481 -->


