---
title: "Data Science - Week 6"
author: "Fay Bennett"
date: "04/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      fig.retina = 3)
```

```{r packages}
library(tidyverse)
```

# Introduction:
We decided to analyze if there is a difference between chaffinch sex and mass.

# Methods:
We compared the difference between chaffinch sex and mass using RStudio and RMarkdown.

# Results:

# Discussion:



<!-- # Importing the dataset: -->
chaff <- read.table("chaff.txt", header = TRUE)

<!-- tidying the data -->
chaff<- chaff%>% 
  pivot_longer(names_to = "sex", 
               values_to = "mass",
               cols = everything())

file <-  "chaff.txt"
write.table(chaff, 
            file, 
            quote = FALSE,
            row.names = FALSE)

<!-- Summarising the data: -->
chaffsummary <- summarySE(chaff, measurevar = "mass", groupvar = "sex")

<!-- calculating the SS(x) of all the mass values: -->
sum_sq <- function(df, measure, group) {
  df %>% group_by({{ group }}) %>% 
    summarise(ss = sum(({{measure}} - mean({{measure}}))^2))
}

sum_sq(chaff, mass, sex)






